Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-05 tex/paper1/paper1.tex
more edits

All these detections algorithms, and many detections in the literature
make either the explicit or implicit {\bf modeling} assumption that
the observed time-series consists of a background trend of some kind
and at least approximately Gaussian-distributed noise.  {\bf The aim
  of this paper is to test the validity of this assumption principally
  in regions of interest to study of the coronal seismology}.  It is
shown below, using data from the Atmospheric Imaging Assembly (AIA,
\citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal emission
may be better described by other models.  These models, {\bf based
  around \PL\ Fourier \PS}, have implications for the practice of
coronal seismology, and may be indicative of the nature of the
fundamental energy deposition that keeps the corona hot.

@@

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  In addition,
  oscillatory power has been identified previously over sunspot
  \citep{}, loop footpoint \citep{} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}

@@

We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

@@

}
\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution (except
$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
that was run took 100,000 samples, with burn-in assumed to be at
50,000 samples.  The chain is thinned by taking every fifth element in
the chain, forming the final sample from which the parameter estimates
and their uncertainties are calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $\exp(-10) \rightarrow \exp(10)$ &  $\exp(-10) \rightarrow \exp(10)$\\
$n$ & $1\rightarrow 6$   & $1\rightarrow 6$  \\
$C$ & $\exp(-20) \rightarrow \exp(10)$  & $\exp(-20) \rightarrow \exp(10)$  \\
$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ & not applicable  & $0.5 - 10$ (mHz)\tablenotemark{1}\\
$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of
frequency)\\
$N_{eff}$ & empirically determined & empirically determined\tablenotemark{2} \\
\enddata
\tablenotetext{1}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
distribution to lie within the prior range.}
\tablenotetext{2}{See Figure \ref{???} and Equation \ref{eqn:neff}.}
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

>>>>

All these detections algorithms, and many detections in the literature
make either the explicit or implicit {\bf modeling} assumption that
the observed time-series consists of a background trend of some kind
and at least approximately Gaussian-distributed noise.  {\bf The aim
  of this paper is to investigate the nature of the Fourier power
  spectrum in regions of interest to study of the coronal seismology,
  thereby testing the assumption above}.  It is shown below, using
data from the Atmospheric Imaging Assembly (AIA,
\citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal
emission may be better described by other models{\bf , based power-law
  power spectra that are actually observed} .  These models, {\bf
  based around \PL\ Fourier \PS}, have implications for the practice
of coronal seismology, and may be indicative of the nature of the
fundamental energy deposition that keeps the corona hot.

@@

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  In addition,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}

@@

{\bf \PL\ \PS\ have been observed in other solar phenomena.}

We hypothesize that the \PL\ \PS\ in the coronal 171\AA\ and
193\AA\ emission is due to the sum of a distribution of a large number
of events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

@@

}
\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution (except
$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
that was run took 100,000 samples, with burn-in assumed to be at
50,000 samples.  The chain is thinned by taking every fifth element in
the chain, forming the final sample from which the parameter estimates
and their uncertainties are calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1 and 2} &
\colhead{Model 2 only} \\
}
\startdata
$\ln(A)$ & $-10 \rightarrow \ln(10)$  & \\
$n$ & $1\rightarrow 6$ &   \\
$\ln(C)$ & $-20 \rightarrow 10$ & \\
$N_{eff}$ & {empirically determined}\tablenotemark{1} & \\
$\ln(\alpha)$  &  & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ &  & $0.5 - 10$ (mHz)\tablenotemark{2}\\
$\log_{10}\delta$ &  & $0.001\rightarrow 3$ \\
\enddata
\tablenotetext{1}{See Figure \ref{???} and Equation \ref{eqn:neff}.}
\tablenotetext{2}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
distribution to lie within the prior range.}
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.
